### 2015-07-09 narrative/data-description.tex
reference fixes

\paragraph{State of the art:}
Our current data annotation techniques demonstrated in
ADIOS~\cite{lofstead:2009:adaptible} implement a binary-packed (BP) data format that
allows data characteristics such as min, max and index to be wrapped around
data chunks. A direct benefit is that each data chunk can be operated upon
independently and I/O concurrency can be maximized. We will build upon this
capability and further augment the format to express data utility.
Recently,
DAMSEL~\cite{damsel} has provided a rich metadata representation and management
layer that captures the relationship between data blocks for scientific
applications.  This allows application data to be mapped to storage system
efficiently, without overburdening users with the management of complex data models, such
as adaptive mesh refinement (AMR), from the user space. 
FFS~\cite{ffs} implements a type system that provides highly efficient binary
data communication and XML-like data description, facilitating data sharing
between collaborators. Additionally, NetCDF~\cite{netcdf} and HDF5~\cite{hdf5}
uses a fixed data format to provide a hierarchical data descriptions for scientific data.
Despite these efforts, the aspect of data importance has yet to be 
explored, and we believe it will be vital for exascale storage solutions.

>>>>

\paragraph{State of the art:}
Our current data annotation techniques demonstrated in
ADIOS~\cite{lofstead:2009:adaptible} implement a binary-packed data format that
allows data characteristics such as min, max and index to be wrapped around
data chunks. A direct benefit is that each data chunk can be operated upon
independently and I/O concurrency can be maximized. We will build upon this
capability and further augment the format to express data utility.
Recently,
DAMSEL~\cite{damsel} has provided a rich metadata representation and management
layer that captures the relationship between data blocks for scientific
applications.  This allows application data to be mapped to storage system
efficiently, without overburdening users with the management of complex data models, such
as AMR, from the user space. Despite these efforts, the aspect of data importance has yet to be 
explored, and we believe it will be vital for exascale storage solutions.
